Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2014-12-15 doc/GMP2015/s03_drp.tex
Change to figure.

@@

\begin{tikzpicture}
    \tikzstyle{v}=[draw, circle, minimum size=0.75cm]
    \tikzstyle{e}=[]

@@

\caption{Two doublets ($C2\times C3$), $\{a_1,a_2,a_3,b_1,b_2,b_3\}$ and $\{b_1,b_2,b_3,c_1,c_2,c_3\}$, intersecting on the triangle $\{b_1,b_2,b_3\}$. Also showing the optimal DR-plan of the graph if we consider it to be a 2D graph; omits further decomposition of the three triangles into their edges and of edges into their individual nodes.}
\label{doublets}
\end{figure*}

>>>>

\begin{figure*}\centering
\begin{subfigure}{.3\linewidth}
  \centering
  \begin{tikzpicture}[scale=2]
        \tikzstyle{v}=[draw, circle, minimum size=0.1cm, font=\footnotesize]
        \tikzstyle{e}=[]

@@

    \caption{}
\end{subfigure}%
\begin{subfigure}{.7\linewidth}
    \centering
    \begin{tikzpicture}[scale=.9, transform shape]
        \tikzstyle{v}=[draw, circle, minimum size=0.75cm, font=\footnotesize]
        \tikzstyle{e}=[]

@@

    \caption{}
\end{subfigure}

\caption{(a) Two doublets ($C2\times C3$), $\{a_1,a_2,a_3,b_1,b_2,b_3\}$ and $\{b_1,b_2,b_3,c_1,c_2,c_3\}$, intersecting on the triangle $\{b_1,b_2,b_3\}$. (b) The optimal DR-plan of the graph if we consider it to be a 2D graph; omits further decomposition of the three triangles into their edges and of edges into their individual nodes.}
\label{doublets}
\end{figure*}
